Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Changes

\begin{abstract}
We investigate the notion of causality in modelling stationary time series. Extending on the work by \citet{Tobar:2015:Learning_Stationary}, we present the Causal Gaussian Process Convolution Model (CGPCM). The CGPCM models the kernel of a Gaussian process nonparametrically and has an inductive bias towards causally-generated time series. We develop enhanced variational inference and learning schemes and demonstrate the CGPCM on synthetic and real-world signals.
\end{abstract}

>>>>

\begin{abstract}
% We investigate the notion of causality in modelling stationary time series. Extending on the work by \citet{Tobar:2015:Learning_Stationary}, we present the Causal Gaussian Process Convolution Model (CGPCM). The CGPCM models the kernel of a Gaussian process nonparametrically and has an inductive bias towards causally-generated time series. We develop enhanced variational inference and learning schemes and demonstrate the CGPCM on synthetic and real-world signals.
Extending on the work by \citet{Tobar:2015:Learning_Stationary}, we present the Causal Gaussian Process Convolution Model (CGPCM), a doubly nonparametric model for causal, spectrally complex dynamical phenomena. The CGPCM is a generative model in which white noise is passed through a causal, nonparametric-window moving-average filter, which we show to be equivalent to a Gaussian process with a nonparametric kernel that is biased towards causally-generated signals. We develop enhanced variational inference and learning schemes for the causal and acausal variants of the GPCM that significantly improve statistical accuracy. These modelling and inferential contributions are finally demonstrated on synthetic and real-world signals.
\end{abstract}
